---
title: "FS Production"
author: "Brandon Mayer"
date: "`r Sys.Date()`"
output: html_document
---
Rebuilding the production analysis. VGS export is a combined file of every year production was collected. This requires a compelete rewrite.
File needs to be pulled in -> proper year selected ->  sheets reorganized. 

```{r setup, include=FALSE,echo=FALSE,}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

In preparation, store the VGS5 Bulk export in the Production -> "RAW_Data folder" under the year data was collected. Example: "SRERexl2022"
  -   the name of the file will not be important for this process. 

```{r setup, include=FALSE,echo=FALSE,warning=FALSE}
# File system setup

year <-readline() #just the year. Example: 2023
path <- paste(dirname(path.expand('~')),"/Box/3. Apache-Sitgreaves National Forests/Data/", paste0(year), sep="")
path2 <- paste(path, paste0("/",year,"_sheeted"), sep="");dir.create(path = paste0(path2))

```

Combined, and splits xlsx into CSVs for analysis

```{r,echo=FALSE,warning=FALSE}

path_to_xlsx <- list.files(path,recursive = F, include.dirs = F, pattern = ".xlsx",full.names = T)


read_excel_allsheets <- function(filename, tibble = FALSE) {
    # I prefer straight data.frames
    # but if you like tidyverse tibbles (the default with read_excel)
    # then just pass tibble = TRUE
    sheets <- readxl::excel_sheets(filename)
    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
    if(!tibble) x <- lapply(x, as.data.frame)
    names(x) <- sheets
    x
}
Sheeted_DF_raw <- list()
for (i in 1:length(path_to_xlsx)) {
  Sheeted_DF_raw[i]<- list(read_excel_allsheets(path_to_xlsx[i]))
}
test <- unlist(Sheeted_DF_raw, recursive=FALSE)
Sheeted_DF <- tapply(test, names(test), dplyr::bind_rows)

sheet_names <- names(Sheeted_DF)
# sheet_names <- readxl::excel_sheets(path_to_xlsx)[2:4]
# base <- gsub("\\..*","",basename(path_to_xlsx))
for (j in sheet_names) {
  # j <- sheet_names[2]
  data <- Sheeted_DF[[j]]
  if (j == "Frequency (by quadrat)") {
    name <- "Freq"
  }else if (j == "Comparative Yield") {
    name <- "CY"
  }else if (j == "Point Ground Cover") {
    name <- "PGC"
  }else{
    name <- "DWR"
  }
  data <- data %>% group_split(SiteID)
  for (n in 1:length(data)) {
    date <- gsub("/","",unique(data[[n]]$Date))
    Base <- gsub("/","",unique(data[[n]]$SiteID))
      write.csv(data[[n]], file=paste0(path2,"/",date,"_",Base,"_",name,".csv"))
  }
}
list.files(path2)
```
Save bag weights in the folder with raw data. Make sure the file is saved as a ".csv" file.

```{r}
sheetedfolder <- path2
results <- paste(path,"/Results/", sep="");dir.create(path = paste0(results))
weights <- read.csv(list.files(path,recursive = F, include.dirs = F, pattern = ".csv",full.names = T))
(sumarWeights<-weights %>% group_by(SiteID)%>% summarise(formula =(lm(c(0,Value)~c(0,BagNum)))$coefficients[-1]));sumarWeights$SiteID <- as.character(sumarWeights$SiteID)
```
-----------------------------------------------------------------CY-----------------------------------------------------------------
Load in comparative yield data
```{r}
allCY <- list.files(path = sheetedfolder, pattern = "CY",full.names = T)
for (i in allCY) {
  file<-  read.csv(i) %>% select(Ancestry ,Date, SiteID, Transect, SampleNumber, nValue) # once run all "Rank" columns will be changed in the sheet-ed copies
  write.csv(file,i,row.names = F)
}
CYdf <- data.table::rbindlist(lapply(allCY, data.table::fread))

TranCY <- transform(merge(CYdf, sumarWeights, by=c("SiteID")), 
                    Dry.wt = nValue * formula) %>% na.omit() 
(Production<- TranCY %>% group_by(Ancestry,SiteID)%>% summarise("Production_kg/ha" = round(mean(Dry.wt)*62.5,digits = 2), "Production_lbs/ac" = (round(mean(Dry.wt)*62.5*.9,digits = 2))))

# Where do you plan on  storing the results 
write.csv(Production, paste0(results,"/Production.csv"))

```
----------------------------------------------------------------------------- DWR ------------------------------------------------------------------

```{r}

# allDWR <- list.files(path = "C:/Users/brand/Dropbox/Project_Data/SRER/Production/SRER2020_sheeted", pattern = "DWR",full.names = T)
allDWR <- list.files(path = sheetedfolder, pattern = "DWR",full.names = T)

for (i in allDWR) {
  file<- read.csv(i) %>% select(Ancestry, Date,SiteID, Transect, SampleNumber, SpeciesName, SpeciesSymbol, nValue)
  write.csv(file,i,row.names = F)
}

DWRdf <- data.table::rbindlist(lapply(allDWR, data.table::fread))
```
--------------------------------------------------------------------------- CY x DWR ---------------------------------------------------------------------
Combine dry weight ranks and comparative yield. This pairs the composition from DWR with the yield providing a composition of biomass observed at the site. 

```{r}
CYDW <- TranCY %>% select(SiteID,Transect,SampleNumber, Dry.wt)
CYDWR <- DWRdf %>% full_join(CYDW, by=c("SiteID","Transect","SampleNumber"))
CYDWR <- CYDWR %>% drop_na(nValue)
CYDWR$nValue[CYDWR$nValue == 1] <- .7
CYDWR$nValue[CYDWR$nValue == 2] <- .2
CYDWR$nValue[CYDWR$nValue == 3] <- .1
CYDWR$nValue <- as.numeric(CYDWR$nValue)
CYDWR <- CYDWR %>% mutate(Spec.Dry.wt = nValue*Dry.wt)

# Species list is from the USDA PLANTS list. The file includes family, growth habit and whether the species is native. Additional species can be added if they are not present. Follwo path and edit directly into the file if necessary. 
# SpecList <- read.csv(paste(dirname(path.expand('~')),"/Box/1.Ruyle_lab/1.Project_Data/Specieslist.csv", sep="")) 
# CYDWR <-CYDWR %>% left_join(SpecList, by=c("SpeciesName", "SpeciesSymbol"))
CYDWR[
  order( CYDWR$SiteID, CYDWR$Date ,CYDWR$Transect ,CYDWR$SampleNumber),
] 
CYDWR <- CYDWR %>% mutate(Palatability= case_when(str_detect(SpeciesName,"Muhlenbergia straminea")~"NP",
                                    TRUE~"P"))
CYDWR <- CYDWR %>% filter(Palatability == "P") %>% group_by(SiteID, Date,Transect,SampleNumber) %>% summarise(Spec.Dry.wt = sum(Spec.Dry.wt))
# Production template used for building rotation will use a combination of composition data as well as the literal breakdown of production between each group. 
(AdjustProduct<- CYDWR %>% group_by(SiteID)%>% summarise("DWRAdjustProduction_kg/ha" = round(mean(Spec.Dry.wt)*62.5,digits = 2), "DWRAdjustProduction_lbs/ac" = (round(mean(Spec.Dry.wt)*62.5*.9,digits = 2))))


final <-left_join(Production,AdjustProduct, by = c("SiteID")) 
write.csv(final, paste0(results,"/Production_wDWR.csv"), row.names = F)

```
-------------------------------------------------------------------------- Frequency ----------------------------------------------------------------

```{r}
allFreq <- list.files(path = sheetedfolder, pattern = "Freq",full.names = T)

for (i in allFreq) {
  file<- read.csv(i) %>% select(Date, SiteID, Transect, SampleNumber, SpeciesName, SpeciesSymbol, nValue)
  write.csv(file,i,row.names = F)
}


Freqdf <- data.table::rbindlist(lapply(allFreq, data.table::fread))
Freqdf <-Freqdf %>% group_by(SiteID, SpeciesName) %>% summarise(Count = n())

write.csv(Freqdf, paste0(results,"/Frequency.csv"), row.names = F)
```


------------------------------------------------------------------------------STOP------------------------------------------------------------------------


