---
title: "XDiamond Production Analysis"
author: "Brandon Mayer"
date: "2023-09-27"
output: html_document
---
---
title: "Production Analysis xlx Sheeting"
author: "Brandon Mayer"
date: "`r Sys.Date()`"
output: html_document
---
Rebuilding the production analysis. VGS export is a combined file of every year production was collected. This requires a compelete rewrite.
File needs to be pulled in -> proper year selected ->  sheets reorganized. 

```{r setup, include=FALSE,echo=FALSE,}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

In preparation, store the VGS5 Bulk export in the Production -> RAW_Data folder under the year data was collected. Exp "SRERexl2022"
  -   the name of the file will not be important for this process. 

```{r setup, include=FALSE,echo=FALSE,warning=FALSE}
# File system setup
year <-readline() 
path <- paste(dirname(path.expand('~')),"/Box/1.Ruyle_lab/1.Project_Data/XDiamond/AZGFD_LandSwap/Data/Production/",year, sep="")
path2 <- paste(dirname(path.expand('~')),"/Box/1.Ruyle_lab/1.Project_Data/XDiamond/AZGFD_LandSwap/Data/Production/", paste0(year,"_sheeted"), sep="");dir.create(path = paste0(path2))

```

Combined, and splits xlsx into CSVs for analysis

```{r,echo=FALSE,warning=FALSE}
path_to_xlsx <- list.files(path,recursive = F, include.dirs = F, pattern = ".xlsx",full.names = T) #[2] 
read_excel_allsheets <- function(filename, tibble = FALSE) {
    # I prefer straight data.frames
    # but if you like tidyverse tibbles (the default with read_excel)
    # then just pass tibble = TRUE
    sheets <- readxl::excel_sheets(filename)
    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
    if(!tibble) x <- lapply(x, as.data.frame)
    names(x) <- sheets
    x
}

Sheeted_DF<- read_excel_allsheets(path_to_xlsx)

Sheeted_DF<-lapply(Sheeted_DF, function(x) {  
   data.frame(x) %>%
     mutate(Date = lubridate::mdy(Date), 
            Year = lubridate::year(Date),
            Pasture = gsub(" ","",gsub("Site:","", sub('-.*', '\\1',sub('.*>', '\\1', Ancestry)), fixed = TRUE)),
            Base = paste0(Pasture,"_",gsub("SRER ","",SiteID)))%>% filter(Year == as.numeric(year))})
```


```{r}

sheet_names <- names(Sheeted_DF)
# sheet_names <- readxl::excel_sheets(path_to_xlsx)[2:4]
# base <- gsub("\\..*","",basename(path_to_xlsx))
for (j in sheet_names) {
  # j <- sheet_names[2]
  data <- Sheeted_DF[[j]]
  if (j == "Robel Pole VOM") {
    name <- "RP"
  }else if (j == "Comparative Yield") {
    name <- "CY"
  }else{
    name <- "DWR"
  }
  data <- data %>% group_split(Base)
  for (n in 1:length(data)) {
    date <- unique(data[[n]]$Date)
    Base <- unique(data[[n]]$Base)
      write.csv(data[[n]], file=paste0(path2,"/",date,"_",Base,"_",name,".csv"))
  }
}

list.files(path2)
```
--------------------------------------------------------------Step 2------------------------------------------------------------------
Assign the location of where the .xlsx files were sheeted or if "sheetedfolder" is still in global environment continue to 
"Comparative Yield" step  

```{r}
# sheetedfolder <- "C:/Users/brand/Dropbox/Project_Data/SRER/Production/SRER2021_sheeted"
# sheetedfolder <- readline()
sheetedfolder <- path2
results <- paste(dirname(path.expand('~')),"/Box/1.Ruyle_lab/1.Project_Data/XDiamond/AZGFD_LandSwap/Results/Production/", year, sep="");dir.create(path = paste0(results))


```

----------------------------------------------------------------- CY ----------------------------------------------------------------

```{r}
weights <- read_csv(list.files(dirname(path),pattern = paste0(year,".csv"),full.names = T))

# Incase of formating errors Pasture is fixed as character data
weights$Pasture <- as.character(weights$Pasture) 
weights$Site <- as.character(weights$Site)
weights
# Creates the formula
(sumarWeights<-weights %>% group_by(Pasture, Site)%>% summarise(formula =(lm(c(0,Value)~c(0,BagNum)))$coefficients[-1]));sumarWeights$Site <- as.character(sumarWeights$Site)
```
-----------------------------------------------------------------CY-----------------------------------------------------------------
Load in comparative yield data
```{r}
allCY <- list.files(path = sheetedfolder, pattern = "CY",full.names = T)

for (i in allCY) {
  file <- read.csv(i)
  base<- basename(i) # date_pasture_transect_method.csv
  file$Pasture <- stringr::str_split(unique(file$SiteID),"_",2)[[1]][1]
  file$Site <- stringr::str_split(unique(file$SiteID),"_",2)[[1]][2]
  file<- file %>% select(Date, Pasture,Site, SiteID, SampleNumber, nValue) # once run all "Rank" columns will be changed in the sheet-ed copies
  write.csv(file,i,row.names = F)
}
CYdf <- data.table::rbindlist(lapply(allCY, data.table::fread))
CYdf$Site <- as.character(CYdf$Site) 
TranCY <- transform(merge(CYdf, sumarWeights, by=c("Pasture", "Site")), 
                    Dry.wt = nValue * formula) %>% na.omit() 
Production<- TranCY %>% group_by(Pasture, Site)%>% summarise("Production_kg/ha" = (mean(Dry.wt)*62.5), "Production_lbs/ac" = (round(mean(Dry.wt)*62.5*.9,digits = 2)))
Production <- Production %>% group_by(Pasture) %>% mutate(`Average Production kg/ha` = mean(`Production_kg/ha`),`Average Production lbs/ac` = mean(`Production_lbs/ac`) )
# Where do you plan on  storing the results 
write.csv(Production, paste0(results,"/Production.csv"))
```
------------------------------------------------------------------------ DWR ------------------------------------------------------------------

```{r}

# allDWR <- list.files(path = "C:/Users/brand/Dropbox/Project_Data/SRER/Production/SRER2020_sheeted", pattern = "DWR",full.names = T)
allDWR <- list.files(path = sheetedfolder, pattern = "DWR",full.names = T)

for (i in allDWR) {
  file <- read.csv(i)
  base<- basename(i) # pasture_transect_method.csv
  file$Date <- gsub("_.*","",base)
  file$Pasture <- stringr::str_split(base,"_",3)[[1]][2]
  file$Site <- stringr::str_match(base, ".*_([^\\.]*)\\_.*")[2]
  file<- file %>% select(Date, Pasture, Site, Transect, SampleNumber, SpeciesName, SpeciesSymbol, nValue)
  write.csv(file,i,row.names = F)
}


DWRdf <- data.table::rbindlist(lapply(allDWR, data.table::fread))
```
------------------------------------------------------------------ CY x DWR --------------------------------------------------------------------
Combine dry weight ranks and comparative yield. This pairs the composition from DWR with the yield providing a composition of biomass observed at the site. 

```{r}
CYDW <- TranCY %>% select(Pasture, Site,Transect,SampleNumber, Dry.wt)
CYDWR <- DWRdf %>% full_join(CYDW, by=c("Pasture","Site","Transect","SampleNumber"))

CYDWR$nValue[CYDWR$nValue == 1] <- .7
CYDWR$nValue[CYDWR$nValue == 2] <- .2
CYDWR$nValue[CYDWR$nValue == 3] <- .1
CYDWR$nValue <- as.numeric(CYDWR$nValue)
CYDWR <- CYDWR %>% mutate(Spec.Dry.wt = nValue*Dry.wt)

# Species list is from the USDA PLANTS list. The file includes family, growth habit and whether the species is native. Additional species can be added if they are not present. Follwo path and edit directly into the file if necessary. 
SpecList <- read.csv(paste(dirname(path.expand('~')),"/Box/1.Ruyle_lab/1.Project_Data/Specieslist.csv", sep="")) 
CYDWR <-CYDWR %>% left_join(SpecList, by=c("SpeciesName", "SpeciesSymbol"))
CYDWR[
  order( CYDWR$Date, CYDWR$Pasture ,CYDWR$Site ,CYDWR$Transect ,CYDWR$SampleNumber),
] 
CYDWR <- CYDWR %>% mutate(Native = case_when(str_detect(Native.Status,"(N)")~"Native",
                                    str_detect(Native.Status,"(I)")~"Introduced"),
                 Grammoid = case_when(str_detect(Growth.Habit,"Graminoid")~"Grass",
                                      TRUE~"NotGrass"))
# Production template used for building rotation will use a combination of composition data as well as the literal breakdown of production between each group. 
Comp <- CYDWR %>% group_by(Pasture, Site, Native, Grammoid) %>% summarize(Biomass=sum(Spec.Dry.wt))%>% group_by(Pasture, Site)%>% mutate(Percent = Biomass/sum(Biomass,na.rm = T))
Comp <- Comp[!is.na(Comp$Biomass),]
Comp <- Comp %>% mutate(ProductionType = paste0(Native,Grammoid))%>% ungroup() %>% select(Pasture, Site,ProductionType, Percent)%>% spread(ProductionType, Percent)%>%replace(is.na(.), 0)%>% mutate(TotalPerennialGrassComp = round(IntroducedGrass+NativeGrass,digits = 2),NativeGrass = round(NativeGrass,digits = 2),IntroducedGrass = round(IntroducedGrass,digits = 2)) %>% select(Pasture,Site,TotalPerennialGrassComp,"NativeGrassComp"=NativeGrass,"IntroducedGrassComp" =IntroducedGrass)

Biomass <- CYDWR %>% group_by(Pasture, Site, Native, Grammoid) %>%  summarise("Production_kg/ha" = (sum(Spec.Dry.wt,na.rm = T)/100*62.5), "Production_lbs/ac" = (round(sum(Spec.Dry.wt,na.rm = T)/100*62.5*.9,digits = 2)))
Biomass <- Biomass[!is.na(Biomass$Native),]
Biomass <- Biomass %>% mutate(ProductionType = paste0(Native,Grammoid))%>% ungroup() %>% select(Pasture, Site,ProductionType, `Production_lbs/ac`)%>% spread(ProductionType, `Production_lbs/ac`)%>%replace(is.na(.), 0)%>% mutate(Total = NativeGrass+IntroducedGrass+NativeNotGrass,TotalPPGG=NativeGrass+IntroducedGrass) %>% select(Pasture,Site,"TotalForage"=Total,TotalPPGG,"NativePPGG"=NativeGrass,"IntroducedPPGG"=IntroducedGrass)

final <-left_join(Comp,Biomass, by = c("Pasture", "Site")) %>% select(Pasture, Site, TotalForage,TotalPerennialGrassComp,NativeGrassComp,IntroducedGrassComp,TotalPPGG,NativePPGG,IntroducedPPGG)
write.csv(final, paste0(results,"/final_results.csv"), row.names = F)

CYDWR %>% group_by(Pasture, Site, SpeciesName) %>%  summarise("Production_kg/ha" = (sum(Spec.Dry.wt,na.rm = T)/100*62.5), "Production_lbs/ac" = (round(sum(Spec.Dry.wt,na.rm = T)/100*62.5*.9,digits = 2)))
```
-----------------------------------------------------------------RP-----------------------------------------------------------------
Load in Robel Pole data
```{r}
allRP <- list.files(path = sheetedfolder, pattern = "RP",full.names = T)

for (i in allRP) {
  i <- allRP[1]
  file <- read.csv(i)
  base<- basename(i) # date_pasture_transect_method.csv
  file$Pasture <- stringr::str_split(unique(file$SiteID),"_",2)[[1]][1]
  file$Site <- stringr::str_split(unique(file$SiteID),"_",2)[[1]][2]
  file<- file %>% select(Date, Pasture,Site, SiteID, SampleNumber, nValue) # once run all "Rank" columns will be changed in the sheet-ed copies
  write.csv(file,i,row.names = F)
}
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        c(N    = length2(xx[[col]], na.rm=na.rm),
          mean = mean   (xx[[col]], na.rm=na.rm),
          sd   = sd     (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )

    # Rename the "mean" column    
    datac <- rename(datac, c("mean" = measurevar))

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

    # Confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult

    return(datac)
}

# Where do you plan on  storing the results 
results <- summarySE(data2022, measurevar="Measurement", groupvars=c("Year","Pasture","Site"))
write.csv(results,paste(dirname(path.expand('~')),"/Box/1.Ruyle_lab/1.Project_Data/XDiamond/AZGFD_LandSwap/Results/Structure/",paste0("RP_",year,".csv"), sep=""))
```